[Artifact57] Robust Resource Bounds with\\ Static Analysis and Bayesian Inference

### 2024-03-07 README/step_by_step_instructions.tex
Fleshed out the explanation of how to produce plots and tables

The artifact contains 10 benchmark programs for Hybrid AARA.
%
As listed in Section 7 of the paper, these benchmarks are: \texttt{MapAppend},
\texttt{Concat}, \texttt{InsertionSort2}, \texttt{QuickSort},
\texttt{QuickSelect}, \texttt{MedianOfMedians}, \texttt{ZAlgorithm},
\texttt{BubbleSort}, \texttt{Round}, and \texttt{EvenOddTail}.
%
Inside the artifact, these benchmarks are referred to as \texttt{append},
\texttt{concat}, \texttt{insertion\_sort}, \texttt{quicksort},
\texttt{quickselect}, \texttt{linear\_select}, \texttt{z\_algorithm},
\texttt{bubble\_sort}, \texttt{round}, and \texttt{even\_split\_odd\_tail}.
%
We have tested both data-driven resource analysis and hybrid resource analysis
on the first seven benchmarks, and only data-driven resource analysis on the
remaining three benchmarks.

@@

For each benchmark, the directory \texttt{bin} already contains the experiment
results that we reported in the paper.
%
We will demonstrate how to generate the experiment results from scratch in
\cref{sec:generate experiment results}.

@@

We demonstrate how to create tables and plots in the paper from the experiment
results that are stored in each benchmark's \texttt{bin} directories.

@@

In Table~1 in the paper, the 4\textsuperscript{th} and 5\textsuperscript{th}
columns display the proportions of sound cost bounds inferred by data-driven and
hybrid resource analyses, respectively.
%
To display these two columns, run
\begin{verbatim}
# cd /home/hybrid_aara/benchmark_suite/toolbox
# python3 run_analysis.py soundness
\end{verbatim}

@@

Figure~5 in the paper displays relative errors of 5 selected benchmarks.
%
To create this plot, run
\begin{verbatim}
# cd /home/hybrid_aara/benchmark_suite/toolbox
# python3 visualization_relative_errors.py
\end{verbatim}
%
This command creates a plot and stores it as a file
\texttt{relative\_errors.pdf} inside the directory
\texttt{/home/hybrid\_aara/benchmark\_suite/images}.
%
To view the plot, we first transfer the plot from the Docker container to the
local filesystem.
%
Run the following command in the terminal of your local machine:
\begin{verbatim}
$ docker cp hybrid_aara:/home/hybrid_aara/benchmark_suite/images/relative_errors.pdf 
    <path_to_local_directory>
\end{verbatim}
where the second argument \texttt{<path\_to\_local\_directory>} is the
destination directory on your local filesystem.
%
You can then view it on your local machine.

@@

>>>>

The artifact contains 10 benchmark programs for Hybrid AARA.
%
As listed in Section 7 of the paper, these benchmarks are: \texttt{MapAppend},
\texttt{Concat}, \texttt{InsertionSort2}, \texttt{QuickSort},
\texttt{QuickSelect}, \texttt{MedianOfMedians}, \texttt{ZAlgorithm},
\texttt{BubbleSort}, \texttt{Round}, and \texttt{EvenOddTail}.
%
Inside the artifact, the benchmark \texttt{EvenOddTail} goes by its full name,
\texttt{EvenSplitOddTail}, instead of its shorthand \texttt{EvenOddTail} used
throughout the paper.
%
We have tested both data-driven resource analysis and hybrid resource analysis
on the first seven benchmarks, and only data-driven resource analysis on the
remaining three benchmarks.

@@

@@

In this section, we demonstrate how to create tables and plots in the paper from
the experiment results that are stored in each benchmark's \texttt{bin}
directories.
%
In the Docker container, the directory \texttt{bin} of each benchmark already
contains the experiment results that we reported in the paper.
%
We will later demonstrate how to generate the experiment results from scratch in
\cref{sec:generate experiment results}.

@@

In Table~1 in the paper, the 4\textsuperscript{th} and 5\textsuperscript{th}
columns display the percentages of sound cost bounds inferred by data-driven and
hybrid resource analyses, respectively.
%
To display these two columns, run
\begin{verbatim}
# cd /home/hybrid_aara/benchmark_suite/toolbox
# python3 run_analysis.py soundness
\end{verbatim}

@@

Figure~5 in the paper displays relative errors of 5 selected benchmarks.
%
To create this plot, run
\begin{verbatim}
# cd /home/hybrid_aara/benchmark_suite/toolbox
# python3 run_analysis.py plot_relative_errors
\end{verbatim}
%
This command creates a plot and stores it as a file
\texttt{relative\_errors.pdf} inside the directory
\texttt{/home/hybrid\_aara/benchmark\_suite/images}.
%
To view the plot, we first transfer it from the Docker container to your local
filesystem.
%
Run the following command in the terminal of your local machine:
\begin{verbatim}
$ docker cp hybrid_aara:/home/hybrid_aara/benchmark_suite\
/images/relative_errors.pdf \
<path-to-local-directory>
\end{verbatim}
where the second argument \texttt{<path-to-local-directory>} is a desired
destination directory on your local filesystem.
%
You can then view the plot on your local machine.

\paragraph{Figures~6--24}

For Figures~6--24 in the paper, to create them, run
\begin{verbatim}
# cd /home/hybrid_aara/benchmark_suite/toolbox
# python3 run_analysis.py plot
\end{verbatim}
%
This command creates all plots of inference results and stores them in the
directory \texttt{benchmark\_suite/<benchmark-name>/images}.
%
For example, for hybrid BayesWC performed on \texttt{QuickSort}, we can
find its plot in the file \texttt{inferred\_cost\_bound.pdf} in the directory
\texttt{benchmark\_suite/QuickSort/images/hybrid/bayeswc}.

To view the plot, again, we transfer it from the Docker container to your local
filesystem.
%
Run this command on the terminal of the local machine:
\begin{verbatim}
$ docker cp hybrid_aara:/home/hybrid_aara/benchmark_suite\
/QuickSort/images/hybrid/bayeswc/inferred_cost_bound.pdf \
<path-to-local-directory>
\end{verbatim}
%
You can then view the plot on your local machine.

\paragraph{Tables~2--11}

For Tables~2--11 in the paper, to create and display them on the stdout, run
\begin{verbatim}
# cd /home/hybrid_aara/benchmark_suite/toolbox
# python3 run_analysis.py relative_errors
\end{verbatim}

@@

\subsection{Source Code}
